\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-03-17 chapters/3_algorithm.tex
Update figs. and cityscapes table; noise exp.

\item A cannot-link-constraint defines a mutual exclusion relationship between two nodes in the graph and is used to specify that the these two nodes should not be associated with the same cluster. (the alg. will introduce them dynamically)
\item Define contracted graph from given graph  $\mathcal{G}$ and clustering $\Pi$; explain edge contraction shown in Fig. 2

@@

Given an initial clustering $\Pi$ where each node of the original graph $\mathcal{G}$ represents its own cluster, the algorithm starts by initializing a contracted graph $\mathcal{G}'$ (see Definition \ref{def:contr_graph}) that will represent the clustering $\Pi$ at each iteration of the agglomeration. The algorithm then sorts all edges $e\in E$ by their absolute weight $|W(e)|$ in descending order in a priority queue, so that the most attractive and the most repulsive edges are processed first. It iteratively pops one edge $e_{uv}$ from priority queue and, depending on the value of the priority $\tilde{w}$ associated to $e_{uv}$, does the following. If the edge is attractive and $\tilde{w}>0$, then merge the connected nodes and perform an edge contraction of $e_{uv}$ in $\mathcal{G}'$ (see Sec. \ref{sec:contr_graph_and_CLC} and Fig. \ref{fig:edge_contraction_and_contr_graph}), provided that $e_{uv}$ was not previously flagged as a cannot-link constraint; for every new pair of double edges in $\mathcal{G}'$ update \UPDATE{their priorities} according to one of the update rules listed in Table \ref{tab:linkage-criteria} and update the cannot-link relationships (see example in Fig. \ref{fig:algorithm_with_without_CLC}b from step 3 to 4). If, on the other hand, the edge $e_{uv}$ is repulsive and $\tilde{w}\leq 0$, then flag it as a cannot-link constraint if and only if the algorithm input-option \texttt{addCannotLink} is true and mutual exclusion relationships should be enforced.

@@

            & & &  \thead{NO} & \thead{YES} \\        
            % \cmidrule[0.3em]{3-5}
            % \midrule[0.15em]
            \midrule\midrule
            Sum: & $f(\tilde{w}_1,\tilde{w}_2) = \tilde{w}_1+\tilde{w}_2$ & \thead{Sum Linkage\\Hierarchical Clustering} & \thead{Greedy Additive \\ Edge Contraction \cite{levinkov2017comparative}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} \\ \midrule

>>>>

\item A cannot-link-constraint defines a mutual exclusion relationship between two nodes in the graph and is used to specify that the these two nodes should not be associated with the same cluster. (the alg. will introduce them dynamically)
\item Define contracted graph from given graph  $\mathcal{G}$ and clustering $\Pi$; explain edge contraction shown in Fig. 2 and define \emph{update rule} $f(w_1, w_2)$

@@

Given an initial clustering $\Pi$ where each node of the original graph $\mathcal{G}$ represents its own cluster, the algorithm starts by initializing a contracted graph $\mathcal{G}'$ (see Definition \ref{def:contr_graph}) that will represent the clustering $\Pi$ at each iteration of the agglomeration. The algorithm then sorts all edges $e\in E$ by their absolute weight $|W(e)|$ in descending order in a priority queue, so that the most attractive and the most repulsive edges are processed first. It iteratively pops one edge $e_{uv}$ from priority queue and, depending on the value of the priority $\tilde{w}$ associated to $e_{uv}$, does the following. If the edge is attractive and $\tilde{w}>0$, then merge the connected nodes and perform an edge contraction of $e_{uv}$ in $\mathcal{G}'$ (see Sec. \ref{sec:contr_graph_and_CLC} and Fig. \ref{fig:edge_contraction_and_contr_graph}), provided that $e_{uv}$ was not previously flagged as a cannot-link constraint; for every new pair of double edges in $\mathcal{G}'$ update \UPDATE{their priorities} according to one of the update rules listed in Table \ref{tab:linkage-criteria} and update their cannot-link relationships (see example in Fig. \ref{fig:algorithm_with_without_CLC}b from step 3 to 4). If, on the other hand, the edge $e_{uv}$ is repulsive and $\tilde{w}\leq 0$, then flag it as a cannot-link constraint if and only if the algorithm input-option \texttt{addCannotLink} is true and mutual exclusion relationships should be enforced.

@@

            & & &  \thead{\textsc{No}} & \thead{\textsc{Yes}} \\        
            % \cmidrule[0.3em]{3-5}
            % \midrule[0.15em]
            \midrule\midrule
            Sum: & $f(\tilde{w}_1,\tilde{w}_2) = \tilde{w}_1+\tilde{w}_2$ & \thead{Sum Linkage\\Hierarchical Clustering} & \thead{Greedy Additive \\ Edge Contraction \cite{levinkov2017comparative}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} \\ \midrule

### 2019-03-17 chapters/5_experiments_cityscapes.tex
Update list of update rules and associated algs.
Update figs. and cityscapes table; noise exp.

\begin{table*}
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{c| c| c | c}
        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
\textbf{mean} & False & {\color{ForestGreen} 0.3429 } & {\color{ForestGreen} 0.5516 } \\
% MEAN finetuned affs avg thresh035 use log costs & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
mean & True & {\color{Orange} 0.3154 } & {\color{Orange} 0.5269 } \\
% MEAN constr finetuned affs avg thresh035 use log costs & {\color{Red} 0.3000 } & {\color{Orange} 0.5140 } \\
sum & False & {\color{Red} 0.2590 } & {\color{Red} 0.4450 } \\
% GAEC finetuned affs avg thresh035 dont use log costs & {\color{Red} 0.2371 } & {\color{Red} 0.4187 } \\

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Results on cityscapes validation set (with finetuned affinities)}
    \label{tab:linkage-criteria}
\end{table*}

\begin{table*}
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{c| c| c | c}
        Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
mean & False & {\color{Orange} 0.3359 } & {\color{ForestGreen} 0.5416 } \\
mean & True & {\color{Orange} 0.3315 } & {\color{ForestGreen} 0.5331 } \\
MutexWatershed & True & {\color{Red} 0.2123 } & {\color{Red} 0.3848 } \\
SingleLinkage & False & {\color{Red} 0.1935 } & {\color{Red} 0.3615 } \\
CompleteLinkage & False & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Scores on cityscapes validation set (original affinities trained by GMIS)}
    \label{tab:linkage-criteria}
\end{table*}

% \begin{table*}
%     \centering
%     \begin{subtable}[t!]{0.98\textwidth}\centering
%         \begin{tabular}{c| c | c | c}
% Update rule & \makecell{Use Cannot-Link\\Constraints} & \makecell{Multicut objective} & Runtime (s)\\ \midrule\midrule
% sum & false & \textbf{-150873} & 99 (??) \\
% sum & true & -150873 & 249 \\
% MutexWatershed & false & -150854 & 100 \\
% mean & false & -150850 & 105 \\
% mean & true & -150848 & 244 \\
% max & true & -149441 & 459 \\
% min & true & -147663 & 186 \\
% min & false & -147663 & 82 \\
% max & false & -103614 & \textbf{16} \\
%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Compare update-rules on fruit-fly large graph}
%     \label{tab:linkage-criteria}
% \end{table*}

>>>>

\begin{table}
    \centering
    \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l M{0.25\textwidth} M{0.25\textwidth}}
        \toprule
        & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
        Update rule: & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{Mean}& \textbf{0.343}  & 0.339  \\
GMIS \cite{liu2018affinity} & 0.341 & -  \\
Max &   0.243  &   0.325  \\
Abs. Max. \cite{wolf2018mutex}  & -  & 0.321 \\
Sum \cite{levinkov2017comparative} & 0.313  & 0.319  \\
Min &  0.000    & 0.000  \\
        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{AP scores on the cityscapes validation set for UGACA and different types of update rules. \TODO{PROBLEM: all apart from GMIS uses finetuned affinities... Unfair comparison?} }
    \label{tab:results_cityscapes}
\end{table}

% \begin{table}
%     \centering
%     \begin{subtable}[t!]{0.5\textwidth}\centering
%         \begin{tabular}{c|| c| c| c |c }
%         & \multicolumn{4}{c}{\thead{Add Cannot-Link-Constraints:}} \\
%         & \multicolumn{2}{c}{\thead{\textsc{No}}} & \multicolumn{2}{c}{\thead{\textsc{Yes}}} \\
%          & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
% Sum & 0.55  & {\color{Orange} 0.313 } & 0.55  & {\color{Orange} 0.319 } \\\midrule
% Abs. Max. & 0.45  & {\color{Orange} 0.321 } & & \\\midrule
% \textbf{Mean}& \textbf{0.35 } & {\color{ForestGreen} \textbf{0.343} } & 0.25  & {\color{Orange} 0.339 } \\\midrule

% Max & 0.85 & {\color{Red} 0.243 } & 0.50  & {\color{Orange} 0.325 } \\\midrule
% Min & 0.50  & {\color{Red} 0.000 } & 0.50  & {\color{Red} 0.000 } \\\midrule
% \cite{liu2018affinity} & -  & {\color{ForestGreen} 0.341 } & - & - \\

%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Results on cityscapes validation set (with finetuned affinities). \TODO{Reformat in the usual form, delete colors, less digits}}
%     \label{tab:results_cityscapes}
% \end{table}

% \begin{table*}
%     \centering
%     \begin{subtable}[t!]{0.98\textwidth}\centering
%         \begin{tabular}{c| c| c | c}
%         Update rule & \makecell{Use Cannot-Link\\Constraints} & AP & AP 50\%\\ \midrule\midrule
% GMIS & - & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5465 } \\
% mean & False & {\color{Orange} 0.3359 } & {\color{ForestGreen} 0.5416 } \\
% mean & True & {\color{Orange} 0.3315 } & {\color{ForestGreen} 0.5331 } \\
% MutexWatershed & True & {\color{Red} 0.2123 } & {\color{Red} 0.3848 } \\
% SingleLinkage & False & {\color{Red} 0.1935 } & {\color{Red} 0.3615 } \\
% CompleteLinkage & False & {\color{Red} 0.0000 } & {\color{Red} 0.0000 } \\

%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Scores on cityscapes validation set (original affinities trained by GMIS)}
%     \label{tab:linkage-criteria}
% \end{table*}

### 2019-03-17 chapters/5_experiments_noise.tex
Update figs. and cityscapes table; noise exp.

% !TEX root = ../agglo_clust_review.tex
\begin{figure}
\centering
\includegraphics[width=0.50\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}
\caption{Plot illustrating results with merge-biased noise...}
\end{figure}

\subsection{Noise experiments}
\begin{itemize}
\item Define Perlin/opensimplex noise
\item Present plots
\item Comment about MC energy
\end{itemize}

\begin{figure}
\centering
\includegraphics[width=0.50\textwidth,trim=0.27in 0.27in 0.27in 0.27in,clip]{./figs/split_noise.pdf}
\caption{Plot illustrating results with split-biased noise...}
\end{figure}

>>>>

% !TEX root = ../agglo_clust_review.tex
% 
\begin{figure}
\centering

        \includegraphics[width=0.48\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}

    \caption{The two figures represent the predictions of the CNN a) without added noise, b) with the addition of the merge-biased noise defined in Eq. \ref{eq:opensimplex_noise_def} and c) with split-biased noise. The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries \TODO{Add colorbar?}}
    % \label{fig:isbi-examples}
\end{figure}%

\begin{figure*}
\centering
        \begin{subfigure}[t]{0.48 \textwidth}
        \centering
        \includegraphics[width=0.98\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}

        \caption{Merge-biased opensimplex noise} \label{fig:thresh}
    \end{subfigure}%
    \begin{subfigure}[t]{0.48 \textwidth}
        \centering
        \includegraphics[width=0.98\textwidth,trim=0.29in 0.31in 0.31in 0.31in,clip]{./figs/split_noise.pdf}
        \caption{Split-biased opensimplex noise} \label{fig:ws}
    \end{subfigure}

\caption{Plot illustrating Adapted RAND scores achieved by UGACA and different update rules when noise is added to the edge weights... \TODO{Label which uses only local-neighbors and which uses long-range connections}}\label{fig:noise_merge}
\end{figure*}

\subsection{Noise experiments}
\begin{itemize}
    \item In this section we will quantitatively test the robustness of UGACA by adding noise to the edge weights of the graph and see how different choices of update rules compare.
    \item Among the update rules listed in Table \ref{tab:linkage-criteria}, we will focus only on \emph{sum}, \emph{arithmetic mean} and \emph{absolute maximum}, since they achieved the best scores in the results presented in Sec. \ref{sec:exp_first_comparison}. Before to present the results shown in Fig. \ref{fig:noise_merge}, we will first introduce the type of noise that was added to the edge weights.
\item In the set of experiments presented in this article, edge weights are estimated \UPDATE{by using a CNN that predicts how likely two neighboring pixels are to be part of the same cluster}. Fig. \ref{fig:noisy_affinities}a illustrates the predictions of the CNN. In image processing there are several ways of adding noise to an image, among which the most common are probably  for neighboring pixels in the horizontal direction of Define Perlin/opensimplex noise
\item Present plots
\item Comment about MC energy
\end{itemize}

% \begin{figure}
% \centering
% \includegraphics[width=0.50\textwidth,trim=0.27in 0.27in 0.27in 0.27in,clip]{./figs/noisy_affs.pdf}
% \caption{Illustration of noisy affinities}\label{fig:noisy_affinities}
% \end{figure}

### 2019-03-17 chapters/supplementary.tex
Update list of update rules and associated algs.
Update figs. and cityscapes table; noise exp.

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Comparison of update rules on crop of cremi sample C (sorted by multicut energy) \TODO{Reduce insane amount of numbers. Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime} }
    \label{tab:linkage-criteria}
\end{table*}

>>>>

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Comparison of update rules on crop of cremi sample C (sorted by multicut energy) \TODO{Reduce insane amount of numbers. Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime. Invert ARAND to make it consistent with the plots} }
    \label{tab:results_cremi_crop_C}
\end{table*}

\begin{table}
    \centering
    \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{M{0.1\textwidth}| c| c| c | c }
        \thead{Update \\rule} & \thead{Use Cannot-Link\\ Constraints} & \thead{Bias \\factor $\beta$} & \thead{AP} & \thead{AP 50\%} \\ \midrule\midrule
\multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
 &Yes & 0.55  & {\color{Orange} 0.319 } & {\color{Orange} 0.527 } \\\midrule
Abs. max. &- & 0.45  & {\color{Orange} 0.321 } & {\color{ForestGreen} 0.531 } \\\midrule
\multirow{2}{*}{Mean} &No & 0.35  & {\color{ForestGreen} 0.343 } & {\color{ForestGreen} 0.552 } \\
 &Yes & 0.25  & {\color{Orange} 0.339 } & {\color{ForestGreen} 0.548 } \\\midrule
\multirow{2}{*}{Max} &No & 0.85 & {\color{Red} 0.243 } & {\color{Red} 0.444 } \\
 &Yes & 0.50  & {\color{Orange} 0.325 } & {\color{ForestGreen} 0.530 } \\\midrule
\multirow{2}{*}{Min} &No & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\
 &Yes & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\\midrule
\cite{liu2018affinity} &-  & -  & {\color{ForestGreen} 0.341 } & {\color{ForestGreen} 0.547 } \\
% MEAN & 0.35 & True & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
% MEAN & 0.30 & False & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5457 } \\
% MEAN & 0.40 & - & {\color{ForestGreen} 0.3402 } & {\color{ForestGreen} 0.5502 } \\
% MEANconstr & 0.30 & False & {\color{Orange} 0.3344 } & {\color{ForestGreen} 0.5469 } \\
% MEAN & 0.45 & - & {\color{Orange} 0.3333 } & {\color{ForestGreen} 0.5438 } \\
% MEAN & 0.50 & - & {\color{Orange} 0.3255 } & {\color{ForestGreen} 0.5341 } \\
% greedyFixation & 0.50 & - & {\color{Orange} 0.3180 } & {\color{Orange} 0.5155 } \\
% MEANconstr & 0.20 & False & {\color{Orange} 0.3161 } & {\color{Orange} 0.5136 } \\
% MutexWatershed & 0.50 & - & {\color{Orange} 0.3158 } & {\color{Orange} 0.5246 } \\
% MEANconstr & 0.35 & False & {\color{Orange} 0.3154 } & {\color{Orange} 0.5269 } \\
% greedyFixation & 0.60 & - & {\color{Orange} 0.3135 } & {\color{Orange} 0.5196 } \\
% GAEC & 0.50 & - & {\color{Orange} 0.3112 } & {\color{Orange} 0.5085 } \\
% SingleLinkagePlusCLC & 0.45 & - & {\color{Orange} 0.3109 } & {\color{Orange} 0.5134 } \\
% GAEC & 0.60 & - & {\color{Orange} 0.3100 } & {\color{Orange} 0.5120 } \\
% greedyFixation & 0.65 & - & {\color{Orange} 0.3056 } & {\color{Orange} 0.5063 } \\
% greedyFixation & 0.45 & - & {\color{Orange} 0.3045 } & {\color{Red} 0.4989 } \\
% GAEC & 0.65 & - & {\color{Orange} 0.3035 } & {\color{Orange} 0.5072 } \\
% GAEC & 0.45 & - & {\color{Orange} 0.3008 } & {\color{Red} 0.4956 } \\
% MEANconstr & 0.35 & True & {\color{Red} 0.3000 } & {\color{Orange} 0.5140 } \\
% MEANconstr & 0.40 & False & {\color{Red} 0.2983 } & {\color{Orange} 0.5076 } \\
% GAEC & 0.70 & - & {\color{Red} 0.2943 } & {\color{Red} 0.4989 } \\
% SingleLinkagePlusCLC & 0.55 & - & {\color{Red} 0.2942 } & {\color{Orange} 0.5074 } \\
% greedyFixation & 0.70 & - & {\color{Red} 0.2919 } & {\color{Red} 0.4906 } \\
% GAEC & 0.75 & - & {\color{Red} 0.2793 } & {\color{Red} 0.4784 } \\
% greedyFixation & 0.75 & - & {\color{Red} 0.2750 } & {\color{Red} 0.4707 } \\
% SingleLinkagePlusCLC & 0.60 & - & {\color{Red} 0.2681 } & {\color{Red} 0.4744 } \\
% GAEC & 0.35 & True & {\color{Red} 0.2590 } & {\color{Red} 0.4450 } \\
% greedyFixation & 0.35 & - & {\color{Red} 0.2587 } & {\color{Red} 0.4484 } \\
% MutexWatershed & 0.40 & - & {\color{Red} 0.2562 } & {\color{Red} 0.4505 } \\
% MEANconstr & 0.50 & - & {\color{Red} 0.2507 } & {\color{Red} 0.4443 } \\
% SingleLinkagePlusCLC & 0.40 & - & {\color{Red} 0.2490 } & {\color{Red} 0.4411 } \\
% SingleLinkagePlusCLC & 0.65 & - & {\color{Red} 0.2489 } & {\color{Red} 0.4401 } \\
% greedyFixation & 0.35 & - & {\color{Red} 0.2438 } & {\color{Red} 0.4297 } \\
% GAEC & 0.35 & False & {\color{Red} 0.2371 } & {\color{Red} 0.4187 } \\
% SingleLinkage & 0.80 & - & {\color{Red} 0.2336 } & {\color{Red} 0.4265 } \\
% SingleLinkagePlusCLC & 0.70 & - & {\color{Red} 0.2285 } & {\color{Red} 0.4045 } \\
% SingleLinkage & 0.75 & - & {\color{Red} 0.2265 } & {\color{Red} 0.4065 } \\
% MutexWatershed & 0.35 & - & {\color{Red} 0.2253 } & {\color{Red} 0.4004 } \\
% SingleLinkage & 0.70 & - & {\color{Red} 0.2213 } & {\color{Red} 0.3947 } \\
% SingleLinkagePlusCLC & 0.35 & - & {\color{Red} 0.2213 } & {\color{Red} 0.3954 } \\
% SingleLinkage & 0.65 & - & {\color{Red} 0.2177 } & {\color{Red} 0.3889 } \\
% SingleLinkage & 0.60 & - & {\color{Red} 0.2116 } & {\color{Red} 0.3842 } \\
% SingleLinkagePlusCLC & 0.75 & - & {\color{Red} 0.2093 } & {\color{Red} 0.3785 } \\
% SingleLinkage & 0.55 & - & {\color{Red} 0.1987 } & {\color{Red} 0.3700 } \\
% SingleLinkage & 0.50 & - & {\color{Red} 0.1952 } & {\color{Red} 0.3659 } \\
% SingleLinkage & 0.35 & - & {\color{Red} 0.1852 } & {\color{Red} 0.3463 } \\

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Results on cityscapes validation set (with finetuned affinities). \TODO{Reformat in the usual form, delete colors, less digits}}
    \label{tab:results_cityscapes_full}
\end{table}
